Understanding domestic abuse

### 2019-07-23 case_for_support_TM_hacked.tex
Anna update

 The findings from this work will result in a high impact journal paper focussing upon the social and interpersonal relationship patterns as well as socio-economic risk factors of domestic abuse victimisation. The target journals for this work are the Journal of Personality and Social Psychology, Social Psychological and Personality Sciences, Journal of Research in Crime and Delinquency, and Personality and Social Psychology Bulletin. \AT{most social psychology journals seem a bit too experimental for this}

@@

 These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes.

 \section{Publication Plan}

 \TM{Developmental Psychology Journals?}
 \AT{publication plan. The Lancet Public Health. Annual Review of Public Health. American Journal of Public Health.}

@@

These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK. \AT{publication plan. fancy behav journals? Nature Human Behaviour, PNAS}

>>>>

 The findings from this work will result in high impact journal papers focussing upon the socio-economic risk factors of domestic abuse victimisation and the social and interpersonal relationship patterns predicting serious harm. The target journals for these works are the Journal of Personality and Social Psychology, Social Psychological and Personality Sciences, Journal of Research in Crime and Delinquency, and Personality and Social Psychology Bulletin.

@@

 These analyses will consist the first UK-based comprehensive quantitative exploration of the causal effect of domestic abuse and childhood abuse on socio-economic outcomes. The resulting paper will be targeted at The Lancet Public Health, and Social Science and Medicine.

% \TM{Developmental Psychology Journals?}
% \AT{publication plan. The Lancet Public Health. Annual Review of Public Health. American Journal of Public Health.}

@@

These analyses will constitute the first extensive analysis of the neighbourhood-level predictors of domestic abuse within the UK. We envisage two articles. One will be focussed upon general behavioural theory and the effect of the environment. This will be targeted towards Nature Human Behaviour, and Proceedings of the National Acedemy of Sciences. The other article will focus upon the implications for criminology and policing. The target journal will be Criminology.

% \AT{publication plan. fancy behav journals? Nature Human Behaviour, PNAS}
